Reducing Acceptance Marks\\ in Emerson-Lei Automata by QBF-solving

### 2022-02-21 paper/main.tex
back to lipics, new abstract

\documentclass[runningheads]{llncs}

% \usepackage[numbers]{natbib}
% \renewcommand\bibsection{\section*{\refname}\small\renewcommand\bibnumfmt[1]{##1.}}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts,amssymb}
\usepackage{hyperref}
% \usepackage{xspace}
% \usepackage{amsthm}
% \usepackage{enumitem} % topsep

@@

\newcommand{\Nset}{{\mathbb{N}_0}}
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\def\Inf{\ensuremath{\mathsf{Inf}}}
\def\Fin{\ensuremath{\mathsf{Fin}}}
\def\false{\mathit{false}}
\def\true{\mathit{true}}
\newcommand{\mA}{\mathcal{A}}
\newcommand{\mB}{\mathcal{B}}
%}}}

@@

\begin{abstract}
  The formalism called \emph{transition-based Emerson-Lei automata
    (TELA)} generalizes many traditional kinds of automata over
  infinite words including Büchi, co-Büchi, Rabin, Streett, and parity
  automata. Transitions in a TELA are marked with acceptance marks and
  its accepting formula is a positive Boolean combination of terms
  saying that a particular mark has to be visited infinitely or
  finitely often in an accepting run. Algorithms processing these
  automata can be very sensitive to the number of different acceptance
  marks. We introduce a new technique reducing the number of
  acceptance marks in a TELA with use of QBF solving. The technique
  produces QBF formulas

  \textbf{Honza je tu}

  without altering its structure and the
  represented language. The technique constructs a \emph{quantified
    Boolean formula (QBF)}

  whose satisfiebility impli a QBF formula parametrized
  which is satisfiable only if

  solver for an
  acceptance condition with fewer acceptance marks and the placement
  of these marks in the automaton structure. Both techniques are
  implemented and experiments show that the number of acceptance marks
  in TELA produced by state-of-the-art tools Delag, ltl3tela, Rabinizer~4,
  and SPOT can be sometimes reduced. In the case of Rabinizer~4, we
  reduced the cummulative number of acceptance marks to less than one
  half.
\end{abstract}

@@

>>>>

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
%\documentclass[a4paper,UKenglish,cleveref, autoref, anonymous, thm-restate]{lipics-v2021}
%
%This is a template for producing LIPIcs articles. 
%See lipics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository% \usepackage[numbers]{natbib}

\bibliographystyle{plainurl}% the mandatory bibstyle

@@

\newcommand{\Nset}{{\mathbb{N}_0}}
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\def\Inf{\ensuremath{\mathsf{Inf}}}
\def\Fin{\ensuremath{\mathsf{Fin}}}
\def\false{\mathit{false}}
\def\true{\mathit{true}}
\newcommand{\mA}{\mathcal{A}}
\newcommand{\mB}{\mathcal{B}}

\title{Reducing Acceptance Marks\\ in Emerson-Lei Automata by QBF-solving}
\author{Tereza Schwarzov\'{a}}{Faculty of Informatics, Masaryk University, Brno, Czech Republic}{xschwar3@mail.muni.cz}{}{}
\author{Jan Strej\v{c}ek}{Faculty of Informatics, Masaryk University, Brno, Czech Republic}{strejcek@fi.muni.cz}{https://orcid.org/0000-0001-5873-403X}{}
\author{Juraj Major}{Faculty of Informatics, Masaryk University, Brno, Czech Republic}{major@fi.muni.cz}{}{}
\authorrunning{T. Schwarzov\'{a}, J. Strej\v{c}ek, and J. Major}
\Copyright{Tereza Schwarzov\'{a}, Jan Strej\v{c}ek, and Juraj Major}
\ccsdesc[500]{Theory of computation~Logic}
\ccsdesc[500]{Theory of computation~Automata over infinite objects}
\keywords{Emerson-Lei automata, TELA, automata reduction, QBF, \todo{telatko?}}
\funding{This work has been supported by the Czech Science Foundation grant GA19-24397S.}

@@

\begin{abstract}
  \emph{Transition-based Emerson-Lei automata (TELA)} become a popular
  formalism that generalizes many traditional kinds of automata over
  infinite words including Büchi, co-Büchi, Rabin, Streett, and parity
  automata. Transitions in a TELA are labelled with acceptance marks
  and its accepting formula is a positive Boolean combination of terms
  saying that a particular mark has to be visited infinitely or
  finitely often in an accepting run. Algorithms processing these
  automata are often very sensitive to the number of different
  acceptance marks. We introduce a new technique reducing the number
  of different acceptance marks in a TELA with use of \emph{quantified
    Boolean formulas (QBF)}: if a constructed QBF formula is
  satisfiable then its model encodes an equivalent accepting formula
  with less acceptance marks. In fact, we present three formula
  constructions trading the speed of the technique for higher
  reduction efficiency. The technique is implemented and evaluated on
  TELA produced by state-of-the-art tools Delag, ltl3tela,
  Rabinizer~4, and SPOT. The technique reduced some acceptance marks
  in automata produced by all these tools. In the case of Rabinizer~4,
  the technique reduced the cummulative number of acceptance marks to
  less than one half. 
\end{abstract}

@@

\todo{Nezapomenout na clanky o redukci automatu pomoci SATu - on virtue of patience?}

### 2022-02-21 paper/main_llncs.tex
back to lipics, new abstract

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
%\documentclass[a4paper,UKenglish,cleveref, autoref, anonymous, thm-restate]{lipics-v2021}
%
%This is a template for producing LIPIcs articles. 
%See lipics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository% \usepackage[numbers]{natbib}

\bibliographystyle{plainurl}% the mandatory bibstyle

@@

\newcommand{\Nset}{{\mathbb{N}_0}}
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\def\Inf{\ensuremath{\mathsf{Inf}}}
\def\Fin{\ensuremath{\mathsf{Fin}}}
\def\false{\mathit{false}}
\def\true{\mathit{true}}
\newcommand{\mA}{\mathcal{A}}
\newcommand{\mB}{\mathcal{B}}

@@

\title{Reducing Acceptance Marks\\ in Emerson-Lei Automata by QBF-solving}
\author{Tereza Schwarzov\'{a}}{Faculty of Informatics, Masaryk University, Brno, Czech Republic}{xschwar3@mail.muni.cz}{}{}
\author{Jan Strej\v{c}ek}{Faculty of Informatics, Masaryk University, Brno, Czech Republic}{strejcek@fi.muni.cz}{https://orcid.org/0000-0001-5873-403X}{}
\author{Juraj Major}{Faculty of Informatics, Masaryk University, Brno, Czech Republic}{major@fi.muni.cz}{}{}
\authorrunning{T. Schwarzov\'{a}, J. Strej\v{c}ek, and J. Major}
\Copyright{Tereza Schwarzov\'{a}, Jan Strej\v{c}ek, and Juraj Major}
\ccsdesc[500]{Theory of computation~Logic}
\ccsdesc[500]{Theory of computation~Automata over infinite objects}
\keywords{Emerson-Lei automata, TELA, automata reduction, QBF, \todo{telatko?}}
\funding{This work has been supported by the Czech Science Foundation grant GA19-24397S.}

@@

\todo{Nezapomenout na clanky o redukci automatu pomoci SATu - on virtue of patience?}

@@

%\bibliographystyle{plain}
\bibliography{mc}

>>>>

\documentclass[runningheads]{llncs}

% \usepackage[numbers]{natbib}
% \renewcommand\bibsection{\section*{\refname}\small\renewcommand\bibnumfmt[1]{##1.}}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts,amssymb}
\usepackage{hyperref}
% \usepackage{xspace}
% \usepackage{amsthm}
% \usepackage{enumitem} % topsep

@@

\newcommand{\Nset}{{\mathbb{N}_0}}
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\def\Inf{\ensuremath{\mathsf{Inf}}}
\def\Fin{\ensuremath{\mathsf{Fin}}}
\def\false{\mathit{false}}
\def\true{\mathit{true}}
\newcommand{\mA}{\mathcal{A}}
\newcommand{\mB}{\mathcal{B}}
%}}}

\title{Reducing Acceptance Marks\\ in Emerson-Lei Automata by QBF-solving}
\authorrunning{J.~Major, T.~Schwarzová and J. Strej\v{c}ek}
 \author{Juraj Major \and Tereza Schwarzová \and Jan Strej\v{c}ek}
 \institute{%
   Masaryk University, Brno, Czech Republic\\ \email{\{major,xschwar3,strejcek\}@fi.muni.cz}
 }

@@

@@

@@

%\bibliographystyle{abbrvnat}
\bibliographystyle{plain}
\bibliography{mc}
